Real-Time Systems

### 2013-10-04 beamer/dit-paper-presentation.tex
renamed module to lowercase (crazy convention following while we can)

	\section{Related works}

@@

    \begin{frame}{Demand-bound function feasibility test}
        \begin{block}{Demand-bound function}
            The \textbf{demand-bound function (DBF)}
            defined for a task set $\tau$ in a time interval $[t_1, t_2]$, denoted $\dbf{t_1, t_2}$, is
            the maximal cumulated execution time of jobs of $\tau$ contained in the
            closed interval $[t_1, t_2]$.
        \end{block}
        $$\dbf{t_1, t_2} = \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i$$
        where $n_i(t_1, t_2)$ is the number of jobs of task $\tau_i$ whose arrival times
        and deadlines are both in the closed interval $[t_1, t_2]$.

@@

    \begin{frame}{Description using the DBF test}
    The DBF test gives us a set of constraints
    $$\dbf{t_1, t_2} \leqslant t_2 - t_1 \; \forall t_1 \leq t_2$$

@@

	\begin{frame}{Definition of the FPDIT}
        \begin{block}{Definitive Idle Time}
            A \textbf{definitive idle time} (DIT) \cite{lipariaverage} is a time $t$ (if it exists) such that every job released strictly before instant $t$ has its absolute deadline before or at instant $t$.
        \end{block}

@@

    \begin{frame}{Finding the FPDIT value - Gauss's Algorithm}
        For given values of $a_i$, if the periods are pairwise coprime, equation~(\ref{eq:FPDIT}) has one solution modulo $H$ given by:

@@

    \begin{frame}{Non-pairwise co-prime moduli}
        If the periods are non-pairwise co-prime, the system has a FPDIT if and only if the following condition is respected:
        \[
            a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i,
            T_j)) \; \forall i,j
        \]

@@

\bibliographystyle{IEEEtran}
\bibliography{dit-paper}

>>>>

	\section{Previous works}

@@

    \begin{frame}{Demand-bound function feasibility test}
        \begin{block}{Demand-bound function}
            The \textbf{demand-bound function (DBF)} \cite{baruah1999generalized,
        baruah1990algorithms}
            defined for a task set $\tau$ in a time interval $[t_1, t_2]$, denoted $\dbf{t_1, t_2}$, is
            the maximal cumulated execution time of jobs of $\tau$ contained in the
            closed interval $[t_1, t_2]$.
        \end{block}
        $$\dbf{t_1, t_2} = \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i$$
        where $n_i(t_1, t_2)$ is the number of jobs of task $\tau_i$ whose arrival times
        and deadlines are both in the closed interval $[t_1, t_2]$.

@@

    \begin{frame}{Description using the DBF test}
    The DBF test gives us a set of constraints to describe the C-space
    $$\dbf{t_1, t_2} \leqslant t_2 - t_1 \; \forall t_1 \leq t_2$$

@@

	\begin{frame}{Definition of the FPDIT}
        \begin{block}{Definitive Idle Time}
            A \textbf{definitive idle time} (DIT) \cite{lipariaverage} is a time $t$ such that every job released strictly before instant $t$ has its absolute deadline before or at instant $t$.
        \end{block}

@@

    \begin{frame}{Finding the FPDIT value - Gauss's Algorithm}
        For given values of $a_i$, if the periods are pairwise coprime, the value of a DIT is given by:

@@

    \begin{frame}{Non-pairwise co-prime moduli}
        If the periods are non-pairwise co-prime, the system has a DIT for given values of $a_i$ if and only if the following condition is respected:
        \[
            a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i,
            T_j)) \; \forall i,j
        \]

@@

\bibliographystyle{amsalpha}
\bibliography{dit-paper}
